---
title: "NCRMP Carbonate Budget"
author: "john morris"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    number_sections: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
editor_options:
  chunk_output_type: console
params:
  rootFolder: "/Users/john.morris/Desktop/projections/ReefPersistenceTool/analysis"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)

`%||%` <- function(x, y) if (!is.null(x) && length(x) > 0 && !all(is.na(x))) x else y
```

```{r loadPackages, echo=FALSE}

library(tidyverse)
library(readr)
library(ggplot2)
```

```{r read Data and define output directory, echo = FALSE}

ncrmp_data <- read_csv(
  file.path(params$rootFolder, "NCRMP_CarbonateBudgets_2014_to_2024.csv"),
  show_col_types = FALSE
)

# Toggle figure export here:
# TRUE  = export PNG and SVG files
# FALSE = do not export files
export_figures <- FALSE

png_dir <- file.path(params$rootFolder, "png")
svg_dir <- file.path(params$rootFolder, "svg")

if (export_figures) {
  dir.create(png_dir, showWarnings = FALSE, recursive = TRUE)
  dir.create(svg_dir, showWarnings = FALSE, recursive = TRUE)
}

# Quick check
#glimpse(ncrmp_data)
```

```{r regression-plot-function, echo = FALSE}

make_regression_plot <- function(data,
                                 x_var,
                                 x_label,
                                 y_var = "net_G",
                                 y_label = "Net Carbonate Production",
                                 group_var,
                                 color_values,
                                 legend_title,
                                 output_stub,
                                 export_figures = FALSE,
                                 png_dir = NULL,
                                 svg_dir = NULL) {
  
  plot_data <- data %>%
    filter(
      !is.na(.data[[x_var]]),
      !is.na(.data[[y_var]]),
      !is.na(.data[[group_var]])
    )
  
  lm_formula <- as.formula(paste(y_var, "~", x_var))
  lm_fit <- lm(lm_formula, data = plot_data)
  lm_summary <- summary(lm_fit)
  
  intercept <- coef(lm_fit)[1]
  slope <- coef(lm_fit)[2]
  p_value <- lm_summary$coefficients[2, 4]
  
  equation_label <- paste0(
    "y = ",
    round(intercept, 3),
    if_else(slope >= 0, " + ", " - "),
    abs(round(slope, 3)),
    "x"
  )
  
  p_label <- case_when(
    p_value < 0.001 ~ "p < 0.001",
    TRUE ~ paste0("p = ", round(p_value, 3))
  )
  
  annotation_label <- paste0(equation_label, "\n", p_label)
  
  p <- ggplot(
    plot_data,
    aes(
      x = .data[[x_var]],
      y = .data[[y_var]],
      color = .data[[group_var]]
    )
  ) +
    geom_point(size = 1.2, alpha = 0.75) +
    geom_smooth(
      aes(group = 1),
      method = "lm",
      se = TRUE,
      color = "black",
      fill = "grey75",
      linewidth = 0.8
    ) +
    annotate(
      "text",
      x = Inf,
      y = Inf,
      label = annotation_label,
      hjust = 1.1,
      vjust = 1.3,
      size = 4.2
    ) +
    scale_color_manual(
      values = color_values,
      name = legend_title,
      drop = FALSE
    ) +
    labs(
      x = x_label,
      y = y_label
    ) +
    theme_classic(base_size = 14) +
    theme(
      legend.position = "right",
      axis.line = element_line(linewidth = 0.8),
      axis.ticks = element_line(linewidth = 0.7)
    )
  
  if (export_figures) {
    
    ggsave(
      filename = file.path(png_dir, paste0(output_stub, ".png")),
      plot = p,
      width = 8,
      height = 5,
      dpi = 300
    )
    
    ggsave(
      filename = file.path(svg_dir, paste0(output_stub, ".svg")),
      plot = p,
      width = 8,
      height = 5
    )
  }
  
  return(p)
}
```

```{r faceted-regression-plot-function, echo = FALSE}

make_faceted_regression_plot <- function(data,
                                         x_var,
                                         x_label,
                                         y_var = "net_G",
                                         y_label = "Net Carbonate Production",
                                         group_var,
                                         color_values,
                                         legend_title,
                                         output_stub,
                                         export_figures = FALSE,
                                         png_dir = NULL,
                                         svg_dir = NULL) {
  
  plot_data <- data %>%
    filter(
      !is.na(.data[[x_var]]),
      !is.na(.data[[y_var]]),
      !is.na(.data[[group_var]])
    )
  
  calc_group_p <- function(df, x_var, y_var) {
    
    if (nrow(df) < 3 || length(unique(df[[x_var]])) < 2) {
      return(NA_real_)
    }
    
    lm_fit <- lm(
      formula = as.formula(paste(y_var, "~", x_var)),
      data = df
    )
    
    lm_summary <- summary(lm_fit)
    
    if (nrow(lm_summary$coefficients) < 2) {
      return(NA_real_)
    }
    
    lm_summary$coefficients[2, 4]
  }
  
  reg_stats <- plot_data %>%
    group_by(.data[[group_var]]) %>%
    group_modify(
      ~ tibble(
        p_value = calc_group_p(.x, x_var = x_var, y_var = y_var)
      )
    ) %>%
    ungroup() %>%
    mutate(
      p_label = case_when(
        is.na(p_value) ~ "p = NA",
        p_value < 0.0001 ~ "p < 0.0001",
        p_value < 0.001 ~ "p < 0.001",
        TRUE ~ paste0("p = ", round(p_value, 3))
      )
    )
  
  p <- ggplot(
    plot_data,
    aes(
      x = .data[[x_var]],
      y = .data[[y_var]],
      color = .data[[group_var]]
    )
  ) +
    geom_hline(
      yintercept = 0,
      linewidth = 0.45,
      color = "grey40"
    ) +
    geom_point(
      size = 1.2,
      alpha = 0.7
    ) +
    geom_smooth(
      method = "lm",
      se = TRUE,
      linewidth = 0.8,
      fill = "grey80",
      alpha = 0.6
    ) +
    geom_text(
      data = reg_stats,
      aes(
        x = Inf,
        y = Inf,
        label = p_label
      ),
      inherit.aes = FALSE,
      hjust = 1.1,
      vjust = 1.3,
      size = 4.2
    ) +
    facet_wrap(
      as.formula(paste("~", group_var))
    ) +
    scale_color_manual(
      values = color_values,
      name = legend_title,
      drop = FALSE
    ) +
    labs(
      x = x_label,
      y = y_label
    ) +
    theme_classic(base_size = 14) +
    theme(
      legend.position = "right",
      strip.background = element_blank(),
      strip.text = element_text(face = "bold", size = 15),
      axis.line = element_line(linewidth = 0.8),
      axis.ticks = element_line(linewidth = 0.7)
    )
  
  if (export_figures) {
    
    ggsave(
      filename = file.path(png_dir, paste0(output_stub, ".png")),
      plot = p,
      width = 10,
      height = 5.5,
      dpi = 300
    )
    
    ggsave(
      filename = file.path(svg_dir, paste0(output_stub, ".svg")),
      plot = p,
      width = 10,
      height = 5.5
    )
  }
  
  return(p)
}
```

```{r regional-lineplot-function, echo = FALSE}

regional_data <- ncrmp_data %>%
  mutate(
    REGION_PLOT = case_when(
      REGION == "SEFCRI" ~ "SEFCRI",
      REGION %in% c("FLK", "FLA KEYS") ~ "FLK",
      REGION == "DRTO" ~ "DRTO",
      TRUE ~ NA_character_
    ),
    REGION_PLOT = factor(
      REGION_PLOT,
      levels = c("SEFCRI", "FLK", "DRTO")
    ),
    YEAR = as.integer(YEAR)
  ) %>%
  filter(!is.na(REGION_PLOT))

# Region colors
region_colors <- c(
  "SEFCRI" = "red3",
  "FLK"    = "green3",
  "DRTO"   = "blue3"
)

# Force x-axis years, including 2020 even though there is no data
year_breaks <- c(2014, 2016, 2018, 2020, 2022, 2024)

make_regional_lineplot <- function(data,
                                   y_var,
                                   y_label,
                                   output_stub,
                                   export_figures = FALSE,
                                   png_dir = NULL,
                                   svg_dir = NULL) {
  
  plot_data <- data %>%
    group_by(YEAR, REGION_PLOT) %>%
    summarise(
      mean_value = mean(.data[[y_var]], na.rm = TRUE),
      sd_value = sd(.data[[y_var]], na.rm = TRUE),
      n = sum(!is.na(.data[[y_var]])),
      se_value = if_else(n > 1, sd_value / sqrt(n), NA_real_),
      .groups = "drop"
    ) %>%
    filter(n > 0)
  
  p <- ggplot(
    plot_data,
    aes(
      x = YEAR,
      y = mean_value,
      color = REGION_PLOT,
      group = REGION_PLOT
    )
  ) +
    geom_line(linewidth = 0.7) +
    geom_point(size = 1.2) +
    geom_errorbar(
      aes(
        ymin = mean_value - se_value,
        ymax = mean_value + se_value
      ),
      width = 0.12,
      linewidth = 0.45,
      na.rm = TRUE
    ) +
    scale_color_manual(
      values = region_colors,
      name = "Region",
      drop = FALSE
    ) +
    scale_x_continuous(
      breaks = year_breaks,
      limits = range(year_breaks)
    ) +
    labs(
      x = "Year",
      y = y_label
    ) +
    theme_classic(base_size = 14) +
    theme(
      legend.position = "right",
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.line = element_line(linewidth = 0.8),
      axis.ticks = element_line(linewidth = 0.7)
    )
  
  if (export_figures) {
    
    ggsave(
      filename = file.path(png_dir, paste0(output_stub, ".png")),
      plot = p,
      width = 8,
      height = 5,
      dpi = 300
    )
    
    ggsave(
      filename = file.path(svg_dir, paste0(output_stub, ".svg")),
      plot = p,
      width = 8,
      height = 5
    )
  }
  
  return(p)
}
```

```{r subregional-lineplot-function, echo = FALSE}

subregional_data <- ncrmp_data %>%
  mutate(
    SUB_REGION_PLOT = case_when(
      SUB_REGION_2 == "SEFCRI" ~ "SEFCRI",
      SUB_REGION_2 == "Biscayne" ~ "BISC",
      SUB_REGION_2 %in% c("Upper Keys", "Upper_Keys") ~ "UK",
      SUB_REGION_2 %in% c("Middle Keys", "Middle_Keys") ~ "MK",
      SUB_REGION_2 %in% c("Lower Keys", "Lower_Keys") ~ "LK",
      SUB_REGION_2 %in% c("Tortugas", "DRTO") ~ "DRTO",
      TRUE ~ NA_character_
    ),
    SUB_REGION_PLOT = factor(
      SUB_REGION_PLOT,
      levels = c("SEFCRI", "BISC", "UK", "MK", "LK", "DRTO")
    ),
    YEAR = as.integer(YEAR)
  ) %>%
  filter(!is.na(SUB_REGION_PLOT))

# Distinct subregion colors
subregion_colors <- c(
  "SEFCRI" = "#D55E00",
  "BISC"   = "#CC79A7",
  "UK"     = "#009E73",
  "MK"     = "#E69F00",
  "LK"     = "#0072B2",
  "DRTO"   = "#000000"
)

# Force x-axis years, including 2020 even though there is no data
year_breaks <- c(2014, 2016, 2018, 2020, 2022, 2024)
make_subregional_lineplot <- function(data,
                                      y_var,
                                      y_label,
                                      output_stub,
                                      export_figures = FALSE,
                                      png_dir = NULL,
                                      svg_dir = NULL) {
  
  plot_data <- data %>%
    group_by(YEAR, SUB_REGION_PLOT) %>%
    summarise(
      mean_value = mean(.data[[y_var]], na.rm = TRUE),
      sd_value = sd(.data[[y_var]], na.rm = TRUE),
      n = sum(!is.na(.data[[y_var]])),
      se_value = if_else(n > 1, sd_value / sqrt(n), NA_real_),
      .groups = "drop"
    ) %>%
    filter(n > 0)
  
  p <- ggplot(
    plot_data,
    aes(
      x = YEAR,
      y = mean_value,
      color = SUB_REGION_PLOT,
      group = SUB_REGION_PLOT
    )
  ) +
    geom_line(linewidth = 0.7) +
    geom_point(size = 1.2) +
    geom_errorbar(
      aes(
        ymin = mean_value - se_value,
        ymax = mean_value + se_value
      ),
      width = 0.12,
      linewidth = 0.45,
      na.rm = TRUE
    ) +
    scale_color_manual(
      values = subregion_colors,
      name = "Sub-region",
      drop = FALSE
    ) +
    scale_x_continuous(
      breaks = year_breaks,
      limits = range(year_breaks)
    ) +
    labs(
      x = "Year",
      y = y_label
    ) +
    theme_classic(base_size = 14) +
    theme(
      legend.position = "right",
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.line = element_line(linewidth = 0.8),
      axis.ticks = element_line(linewidth = 0.7)
    )
  
  if (export_figures) {
    
    ggsave(
      filename = file.path(png_dir, paste0(output_stub, ".png")),
      plot = p,
      width = 8,
      height = 5,
      dpi = 300
    )
    
    ggsave(
      filename = file.path(svg_dir, paste0(output_stub, ".svg")),
      plot = p,
      width = 8,
      height = 5
    )
  }
  
  return(p)
}
```

```{r habitat-type-lineplot-function, echo = FALSE}

habitat_data <- ncrmp_data %>%
  mutate(
    YEAR = as.integer(YEAR),
    
    HABITAT_PLOT = case_when(
      HABITAT_TYPE == "SEFCRI" ~ "SEFCRI",
      HABITAT_TYPE == "Inshore" ~ "Inshore",
      HABITAT_TYPE %in% c("MidChannel", "Mid Channel", "Midchannel") ~ "MidChannel",
      HABITAT_TYPE == "Offshore" ~ "Offshore",
      HABITAT_TYPE == "Lagoon" ~ "Lagoon",
      HABITAT_TYPE %in% c("Forereef", "ForeReef", "Fore Reef") ~ "Forereef",
      HABITAT_TYPE == "Bank" ~ "Bank",
      TRUE ~ NA_character_
    ),
    
    HABITAT_PLOT = factor(
      HABITAT_PLOT,
      levels = c(
        "SEFCRI",
        "Inshore",
        "MidChannel",
        "Offshore",
        "Lagoon",
        "Forereef",
        "Bank"
      )
    ),
    
    SUB_REGION_PLOT = case_when(
      SUB_REGION_2 == "SEFCRI" ~ "SEFCRI",
      SUB_REGION_2 == "Biscayne" ~ "BISC",
      SUB_REGION_2 %in% c("Upper Keys", "Upper_Keys") ~ "UK",
      SUB_REGION_2 %in% c("Middle Keys", "Middle_Keys") ~ "MK",
      SUB_REGION_2 %in% c("Lower Keys", "Lower_Keys") ~ "LK",
      SUB_REGION_2 %in% c("Tortugas", "DRTO") ~ "DRTO",
      TRUE ~ NA_character_
    ),
    
    SUB_REGION_PLOT = factor(
      SUB_REGION_PLOT,
      levels = c("SEFCRI", "BISC", "UK", "MK", "LK", "DRTO")
    )
  ) %>%
  filter(!is.na(HABITAT_PLOT))

# Habitat colors
habitat_colors <- c(
  "SEFCRI"     = "#8B0000",  # dark red
  "Inshore"    = "#E69F00",  # orange/gold
  "MidChannel" = "#009E73",  # green
  "Offshore"   = "#CC79A7",  # purple/pink
  "Lagoon"     = "#56B4E9",  # sky blue
  "Forereef"   = "#0072B2",  # blue
  "Bank"       = "#000000"   # black
)

# FLK-only habitat colors
flk_habitat_colors <- habitat_colors[c("Inshore", "MidChannel", "Offshore")]

# DRTO-only habitat colors
drto_habitat_colors <- habitat_colors[c("Lagoon", "Forereef", "Bank")]

make_habitat_lineplot <- function(data,
                                  y_var,
                                  y_label,
                                  plot_title,
                                  output_stub,
                                  color_values,
                                  export_figures = FALSE,
                                  png_dir = NULL,
                                  svg_dir = NULL) {
  
  plot_data <- data %>%
    filter(
      !is.na(YEAR),
      !is.na(HABITAT_PLOT),
      !is.na(.data[[y_var]])
    ) %>%
    group_by(YEAR, HABITAT_PLOT) %>%
    summarise(
      mean_value = mean(.data[[y_var]], na.rm = TRUE),
      sd_value = sd(.data[[y_var]], na.rm = TRUE),
      n = sum(!is.na(.data[[y_var]])),
      se_value = if_else(n > 1, sd_value / sqrt(n), NA_real_),
      .groups = "drop"
    ) %>%
    filter(n > 0)
  
  p <- ggplot(
    plot_data,
    aes(
      x = YEAR,
      y = mean_value,
      color = HABITAT_PLOT,
      group = HABITAT_PLOT
    )
  ) +
    geom_line(linewidth = 0.7) +
    geom_point(size = 1.2) +
    geom_errorbar(
      aes(
        ymin = mean_value - se_value,
        ymax = mean_value + se_value
      ),
      width = 0.12,
      linewidth = 0.45,
      na.rm = TRUE
    ) +
    scale_color_manual(
      values = color_values,
      name = "Habitat Type",
      drop = FALSE
    ) +
    scale_x_continuous(
      breaks = year_breaks,
      limits = range(year_breaks)
    ) +
    labs(
      title = plot_title,
      x = "Year",
      y = y_label
    ) +
    theme_classic(base_size = 14) +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      legend.position = "right",
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.line = element_line(linewidth = 0.8),
      axis.ticks = element_line(linewidth = 0.7)
    )
  
  if (export_figures) {
    
    ggsave(
      filename = file.path(png_dir, paste0(output_stub, ".png")),
      plot = p,
      width = 8,
      height = 5,
      dpi = 300
    )
    
    ggsave(
      filename = file.path(svg_dir, paste0(output_stub, ".svg")),
      plot = p,
      width = 8,
      height = 5
    )
  }
  
  return(p)
}
```

```{r reef-state-plot-prep, echo = FALSE}

reef_state_levels <- c("Growth", "Stasis", "Erosion")

reef_state_colors <- c(
  "Growth" = "#006400",  # dark green
  "Stasis" = "#B8860B",  # dark yellow / goldenrod
  "Erosion" = "#8B0000"   # dark red
)

reef_state_data <- ncrmp_data %>%
  mutate(
    YEAR = as.integer(YEAR),
    
    budget_State = factor(
      budget_State,
      levels = reef_state_levels
    ),
    
    REGION_PLOT = case_when(
      REGION == "SEFCRI" ~ "SEFCRI",
      REGION %in% c("FLK", "FLA KEYS") ~ "FLK",
      REGION == "DRTO" ~ "DRTO",
      TRUE ~ NA_character_
    ),
    
    REGION_PLOT = factor(
      REGION_PLOT,
      levels = c("SEFCRI", "FLK", "DRTO")
    ),
    
    SUB_REGION_PLOT = case_when(
      SUB_REGION_2 == "SEFCRI" ~ "SEFCRI",
      SUB_REGION_2 == "Biscayne" ~ "BISC",
      SUB_REGION_2 %in% c("Upper Keys", "Upper_Keys") ~ "UK",
      SUB_REGION_2 %in% c("Middle Keys", "Middle_Keys") ~ "MK",
      SUB_REGION_2 %in% c("Lower Keys", "Lower_Keys") ~ "LK",
      SUB_REGION_2 %in% c("Tortugas", "DRTO") ~ "DRTO",
      TRUE ~ NA_character_
    ),
    
    SUB_REGION_PLOT = factor(
      SUB_REGION_PLOT,
      levels = c("SEFCRI", "BISC", "UK", "MK", "LK", "DRTO")
    ),
    
    HABITAT_PLOT = case_when(
      HABITAT_TYPE == "Inshore" ~ "Inshore",
      HABITAT_TYPE %in% c("MidChannel", "Mid Channel", "Midchannel") ~ "MidChannel",
      HABITAT_TYPE == "Offshore" ~ "Offshore",
      HABITAT_TYPE == "Lagoon" ~ "Lagoon",
      HABITAT_TYPE %in% c("Forereef", "ForeReef", "Fore Reef") ~ "Forereef",
      HABITAT_TYPE == "Bank" ~ "Bank",
      TRUE ~ NA_character_
    ),
    
    HABITAT_PLOT = factor(
      HABITAT_PLOT,
      levels = c("Inshore", "MidChannel", "Offshore", "Lagoon", "Forereef", "Bank")
    )
  ) %>%
  filter(!is.na(budget_State))


make_reef_state_barplot <- function(data,
                                    plot_title,
                                    output_stub,
                                    export_figures = FALSE,
                                    png_dir = NULL,
                                    svg_dir = NULL) {
  
  plot_data <- data %>%
    filter(!is.na(YEAR), !is.na(budget_State)) %>%
    count(YEAR, budget_State, name = "site_count") %>%
    complete(
      YEAR = year_breaks,
      budget_State = factor(reef_state_levels, levels = reef_state_levels),
      fill = list(site_count = 0)
    ) %>%
    group_by(YEAR) %>%
    mutate(
      annual_total = sum(site_count),
      annual_proportion = if_else(
        annual_total > 0,
        site_count / annual_total,
        NA_real_
      )
    ) %>%
    ungroup() %>%
    filter(!is.na(annual_proportion))
  
  p <- ggplot(
    plot_data,
    aes(
      x = factor(YEAR, levels = year_breaks),
      y = annual_proportion,
      fill = budget_State
    )
  ) +
    geom_col(
      position = position_dodge(width = 0.8),
      width = 0.7,
      color = "black",
      linewidth = 0.25
    ) +
    scale_fill_manual(
      values = reef_state_colors,
      name = "Budget State",
      drop = FALSE
    ) +
    scale_y_continuous(
      limits = c(0, 1),
      breaks = seq(0, 1, 0.2),
      expand = expansion(mult = c(0, 0.04))
    ) +
    labs(
      title = plot_title,
      x = "Year",
      y = "Annual Proportion"
    ) +
    theme_classic(base_size = 14) +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      legend.position = "right",
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.line = element_line(linewidth = 0.8),
      axis.ticks = element_line(linewidth = 0.7)
    )
  
  if (export_figures) {
    
    ggsave(
      filename = file.path(png_dir, paste0(output_stub, ".png")),
      plot = p,
      width = 8,
      height = 5,
      dpi = 300
    )
    
    ggsave(
      filename = file.path(svg_dir, paste0(output_stub, ".svg")),
      plot = p,
      width = 8,
      height = 5
    )
  }
  
  return(p)
}
```

```{r carbonate-production-barplot-function, echo = FALSE}
make_carbonate_barplot <- function(data,
                                   plot_title,
                                   output_stub,
                                   export_figures = FALSE,
                                   png_dir = NULL,
                                   svg_dir = NULL) {
  
  metric_levels <- c(
    "Net carbonate production",
    "Gross carbonate production",
    "Gross carbonate erosion"
  )
  
  metric_colors <- c(
    "Net carbonate production" = "black",
    "Gross carbonate production" = "white",
    "Gross carbonate erosion" = "grey65"
  )
  
  plot_wide <- data %>%
    filter(
      !is.na(YEAR),
      !is.na(net_G),
      !is.na(grossP_G),
      !is.na(grossE_G)
    ) %>%
    mutate(
      YEAR = factor(as.integer(YEAR), levels = year_breaks),
      
      # Plot gross erosion downward to match carbonate-budget convention
      grossE_G_plot = -abs(grossE_G)
    )
  
  plot_data <- plot_wide %>%
    select(YEAR, net_G, grossP_G, grossE_G_plot) %>%
    pivot_longer(
      cols = c(net_G, grossP_G, grossE_G_plot),
      names_to = "metric",
      values_to = "value"
    ) %>%
    mutate(
      metric = case_when(
        metric == "net_G" ~ "Net carbonate production",
        metric == "grossP_G" ~ "Gross carbonate production",
        metric == "grossE_G_plot" ~ "Gross carbonate erosion",
        TRUE ~ metric
      ),
      metric = factor(metric, levels = metric_levels)
    ) %>%
    group_by(YEAR, metric) %>%
    summarise(
      mean_value = mean(value, na.rm = TRUE),
      sd_value = sd(value, na.rm = TRUE),
      n = sum(!is.na(value)),
      se_value = if_else(n > 1, sd_value / sqrt(n), NA_real_),
      .groups = "drop"
    ) %>%
    filter(n > 0)
  
  n_data <- plot_wide %>%
    group_by(YEAR) %>%
    summarise(
      n_sites = n(),
      .groups = "drop"
    )
  
  y_min <- min(plot_data$mean_value - replace_na(plot_data$se_value, 0), na.rm = TRUE)
  y_max <- max(plot_data$mean_value + replace_na(plot_data$se_value, 0), na.rm = TRUE)
  y_range <- y_max - y_min
  
  if (!is.finite(y_range) || y_range == 0) {
    y_range <- 1
  }
  
  y_limits <- c(
    y_min - 0.15 * y_range,
    y_max + 0.10 * y_range
  )
  
  n_data <- n_data %>%
    mutate(
      metric = factor("Net carbonate production", levels = metric_levels),
      y_pos = y_limits[1] + 0.04 * diff(y_limits),
      n_label = paste0("n=", n_sites)
    )
  
  p <- ggplot(
    plot_data,
    aes(
      x = metric,
      y = mean_value,
      fill = metric
    )
  ) +
    geom_hline(
      yintercept = 0,
      linewidth = 0.45,
      color = "black"
    ) +
    geom_col(
      width = 0.75,
      color = "black",
      linewidth = 0.45
    ) +
    geom_errorbar(
      aes(
        ymin = mean_value - se_value,
        ymax = mean_value + se_value
      ),
      width = 0.20,
      linewidth = 0.45,
      na.rm = TRUE
    ) +
    geom_text(
      data = n_data,
      aes(
        x = metric,
        y = y_pos,
        label = n_label
      ),
      inherit.aes = FALSE,
      hjust = 0,
      size = 3.7
    ) +
    facet_wrap(
      ~ YEAR,
      nrow = 1,
      drop = TRUE
    ) +
    scale_fill_manual(
      values = metric_colors,
      name = NULL,
      drop = FALSE
    ) +
    coord_cartesian(
      ylim = y_limits,
      clip = "off"
    ) +
    labs(
      title = plot_title,
      x = NULL,
      y = "Carbonate Production"
    ) +
    theme_classic(base_size = 14) +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      legend.position = "bottom",
      legend.box = "vertical",
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      strip.background = element_blank(),
      strip.text = element_text(face = "bold", size = 15),
      panel.border = element_rect(color = "black", fill = NA, linewidth = 0.6),
      axis.line = element_line(linewidth = 0.8),
      axis.ticks = element_line(linewidth = 0.7)
    )
  
  if (export_figures) {
    
    ggsave(
      filename = file.path(png_dir, paste0(output_stub, ".png")),
      plot = p,
      width = 11,
      height = 4.8,
      dpi = 300
    )
    
    ggsave(
      filename = file.path(svg_dir, paste0(output_stub, ".svg")),
      plot = p,
      width = 11,
      height = 4.8
    )
  }
  
  return(p)
}
```





# Pooled Data
## Carbonate Budget
```{r pooled-carbonate-production-bars, echo = FALSE, fig.width = 11, fig.height = 4.8}
p_pooled_carbonate_bars <- make_carbonate_barplot(
  data = ncrmp_data,
  plot_title = "Pooled Data - Carbonate Production",
  output_stub = "pooled_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_pooled_carbonate_bars
```

## Budget State
```{r reef-state-pooled, echo = FALSE, fig.width = 8, fig.height = 5}
p_reef_state_pooled <- make_reef_state_barplot(
  data = reef_state_data,
  plot_title = "Pooled Data - Proportional Reef State",
  output_stub = "reef_state_pooled_data",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_reef_state_pooled
```

## Regressions
### Coral Cover
```{r pooled-coral-reg, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_coral_cover_regression <- make_regression_plot(
  data = regional_data,
  x_var = "hardCoral_PrctCvr",
  x_label = "Coral Cover (%)",
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  group_var = "REGION_PLOT",
  color_values = region_colors,
  legend_title = "Region",
  output_stub = "regional_regression_netG_vs_coral_cover",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_coral_cover_regression
```

### Parrotfish Biomass
```{r pooled-parrotBio-reg, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_parrotfish_biomass_regression <- make_regression_plot(
  data = regional_data,
  x_var = "parrotfish_Biomass",
  x_label = "Parrotfish Biomass",
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  group_var = "REGION_PLOT",
  color_values = region_colors,
  legend_title = "Region",
  output_stub = "regional_regression_netG_vs_parrotfish_biomass",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_parrotfish_biomass_regression
```

### Parrotfish Density
```{r pooled-parrotDen-reg, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_parrotfish_density_regression <- make_regression_plot(
  data = regional_data,
  x_var = "parrotfish_Density",
  x_label = "Parrotfish Density",
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  group_var = "REGION_PLOT",
  color_values = region_colors,
  legend_title = "Region",
  output_stub = "regional_regression_netG_vs_parrotfish_density",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_parrotfish_density_regression
```





# Regional
## Carbonate Budget
```{r regional-carbonate-production-bars, echo = FALSE, fig.width = 11, fig.height = 4.8}
p_region_sefcri_carbonate_bars <- make_carbonate_barplot(
  data = regional_data %>% filter(REGION_PLOT == "SEFCRI"),
  plot_title = "SEFCRI - Carbonate Production",
  output_stub = "regional_SEFCRI_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_region_flk_carbonate_bars <- make_carbonate_barplot(
  data = regional_data %>% filter(REGION_PLOT == "FLK"),
  plot_title = "FLK - Carbonate Production",
  output_stub = "regional_FLK_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_region_drto_carbonate_bars <- make_carbonate_barplot(
  data = regional_data %>% filter(REGION_PLOT == "DRTO"),
  plot_title = "DRTO - Carbonate Production",
  output_stub = "regional_DRTO_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

print(p_region_sefcri_carbonate_bars)
print(p_region_flk_carbonate_bars)
print(p_region_drto_carbonate_bars)
```

## Budget State
```{r reef-state-regional, echo = FALSE, fig.width = 8, fig.height = 5}
p_reef_state_region_sefcri <- make_reef_state_barplot(
  data = reef_state_data %>% filter(REGION_PLOT == "SEFCRI"),
  plot_title = "SEFCRI - Proportional Reef State",
  output_stub = "reef_state_region_SEFCRI",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_region_flk <- make_reef_state_barplot(
  data = reef_state_data %>% filter(REGION_PLOT == "FLK"),
  plot_title = "FLK - Proportional Reef State",
  output_stub = "reef_state_region_FLK",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_region_drto <- make_reef_state_barplot(
  data = reef_state_data %>% filter(REGION_PLOT == "DRTO"),
  plot_title = "DRTO - Proportional Reef State",
  output_stub = "reef_state_region_DRTO",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_region_sefcri
p_reef_state_region_flk
p_reef_state_region_drto
```

## Regressions
### Coral Cover
```{r regional-coralCover-reg, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_coral_cover_faceted_regression <- make_faceted_regression_plot(
  data = regional_data,
  x_var = "hardCoral_PrctCvr",
  x_label = "Coral Cover (%)",
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  group_var = "REGION_PLOT",
  color_values = region_colors,
  legend_title = "Region",
  output_stub = "regional_faceted_regression_netG_vs_coral_cover",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_coral_cover_faceted_regression
```

### Parrotfish Biomass
```{r regional-parrotBio-reg, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_parrotfish_biomass_faceted_regression <- make_faceted_regression_plot(
  data = regional_data,
  x_var = "parrotfish_Biomass",
  x_label = "Parrotfish Biomass",
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  group_var = "REGION_PLOT",
  color_values = region_colors,
  legend_title = "Region",
  output_stub = "regional_faceted_regression_netG_vs_parrotfish_biomass",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_parrotfish_biomass_faceted_regression
```

### Parrotfish Density
```{r regional-parrotDen-reg, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_parrotfish_density_faceted_regression <- make_faceted_regression_plot(
  data = regional_data,
  x_var = "parrotfish_Density",
  x_label = "Parrotfish Density",
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  group_var = "REGION_PLOT",
  color_values = region_colors,
  legend_title = "Region",
  output_stub = "regional_faceted_regression_netG_vs_parrotfish_density",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_parrotfish_density_faceted_regression
```

## Temporal Trends
### Net Carbonate Production
```{r regional-net-carbonate-production, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_net_production <- make_regional_lineplot(
  data = regional_data,
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  output_stub = "regional_net_carbonate_production",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_net_production
```

### Coral Cover
```{r regional-coral-cover, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_coral_cover <- make_regional_lineplot(
  data = regional_data,
  y_var = "hardCoral_PrctCvr",
  y_label = "Coral Cover (%)",
  output_stub = "regional_coral_cover",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_coral_cover
```

### Coral Production
```{r regional-coral-carbonate-production, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_coral_production <- make_regional_lineplot(
  data = regional_data,
  y_var = "hardCoral_G",
  y_label = "Coral Carbonate Production",
  output_stub = "regional_coral_carbonate_production",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_coral_production
```

### CCA Cover
```{r regional-cca-cover, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_cca_cover <- make_regional_lineplot(
  data = regional_data,
  y_var = "cca_PrctCvr",
  y_label = "CCA Cover",
  output_stub = "regional_cca_cover",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_cca_cover
```

### CCA Production
```{r regional-cca-production, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_cca_production <- make_regional_lineplot(
  data = regional_data,
  y_var = "cca_G",
  y_label = "CCA Carbonate Production",
  output_stub = "regional_cca_carbonate_production",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_cca_production
```

### Parrotfish Erosion
```{r regional-parrotfish-erosion, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_parrotfish_erosion <- make_regional_lineplot(
  data = regional_data,
  y_var = "parrotfish_G",
  y_label = "Parrotfish Erosion",
  output_stub = "regional_parrotfish_erosion",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_regional_parrotfish_erosion
```

### Parrotfish Biomass
```{r regional-parrotfish-biomass, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_parrotfish_biomass <- make_regional_lineplot(
  data = regional_data,
  y_var = "parrotfish_Biomass",
  y_label = "Parrotfish Biomass",
  output_stub = "regional_parrotfish_biomass",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_parrotfish_biomass
```

### Parrotfish Density
```{r regional-parrotfish-density, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_parrotfish_density <- make_regional_lineplot(
  data = regional_data,
  y_var = "parrotfish_Density",
  y_label = "Parrotfish Density",
  output_stub = "regional_parrotfish_density",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_parrotfish_density
```

### Microbioerosion
```{r regional-microbioerosion, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_microbioerosion <- make_regional_lineplot(
  data = regional_data,
  y_var = "microbioerosion_G",
  y_label = "Microbioerosion",
  output_stub = "regional_microbioerosion",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_microbioerosion
```

### Macrobioerosion
```{r regional-macrobioerosion, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_macrobioerosion <- make_regional_lineplot(
  data = regional_data,
  y_var = "macrobioerosion_G",
  y_label = "Macrobioerosion",
  output_stub = "regional_macrobioerosion",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_macrobioerosion
```

### Urchins
```{r regional-urchins, echo = FALSE, fig.width = 8, fig.height = 5}
p_regional_urchins <- make_regional_lineplot(
  data = regional_data,
  y_var = "urchin_G",
  y_label = "Urchin Erosion",
  output_stub = "regional_urchin_erosion",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_regional_urchins
```




# Sub-Regional
## Carbonate Budget
```{r subregional-carbonate-production-bars, echo = FALSE, fig.width = 11, fig.height = 4.8}
p_subregion_sefcri_carbonate_bars <- make_carbonate_barplot(
  data = subregional_data %>% filter(SUB_REGION_PLOT == "SEFCRI"),
  plot_title = "SEFCRI - Carbonate Production",
  output_stub = "subregional_SEFCRI_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_subregion_bisc_carbonate_bars <- make_carbonate_barplot(
  data = subregional_data %>% filter(SUB_REGION_PLOT == "BISC"),
  plot_title = "BISC - Carbonate Production",
  output_stub = "subregional_BISC_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_subregion_uk_carbonate_bars <- make_carbonate_barplot(
  data = subregional_data %>% filter(SUB_REGION_PLOT == "UK"),
  plot_title = "UK - Carbonate Production",
  output_stub = "subregional_UK_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_subregion_mk_carbonate_bars <- make_carbonate_barplot(
  data = subregional_data %>% filter(SUB_REGION_PLOT == "MK"),
  plot_title = "MK - Carbonate Production",
  output_stub = "subregional_MK_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_subregion_lk_carbonate_bars <- make_carbonate_barplot(
  data = subregional_data %>% filter(SUB_REGION_PLOT == "LK"),
  plot_title = "LK - Carbonate Production",
  output_stub = "subregional_LK_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_subregion_drto_carbonate_bars <- make_carbonate_barplot(
  data = subregional_data %>% filter(SUB_REGION_PLOT == "DRTO"),
  plot_title = "DRTO - Carbonate Production",
  output_stub = "subregional_DRTO_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

print(p_subregion_sefcri_carbonate_bars)
print(p_subregion_bisc_carbonate_bars)
print(p_subregion_uk_carbonate_bars)
print(p_subregion_mk_carbonate_bars)
print(p_subregion_lk_carbonate_bars)
print(p_subregion_drto_carbonate_bars)
```

## Budget State
```{r reef-state-subregional, echo = FALSE, fig.width = 8, fig.height = 5}
p_reef_state_subregion_sefcri <- make_reef_state_barplot(
  data = reef_state_data %>% filter(SUB_REGION_PLOT == "SEFCRI"),
  plot_title = "SEFCRI - Proportional Reef State",
  output_stub = "reef_state_subregion_SEFCRI",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_subregion_bisc <- make_reef_state_barplot(
  data = reef_state_data %>% filter(SUB_REGION_PLOT == "BISC"),
  plot_title = "BISC - Proportional Reef State",
  output_stub = "reef_state_subregion_BISC",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_subregion_uk <- make_reef_state_barplot(
  data = reef_state_data %>% filter(SUB_REGION_PLOT == "UK"),
  plot_title = "UK - Proportional Reef State",
  output_stub = "reef_state_subregion_UK",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_subregion_mk <- make_reef_state_barplot(
  data = reef_state_data %>% filter(SUB_REGION_PLOT == "MK"),
  plot_title = "MK - Proportional Reef State",
  output_stub = "reef_state_subregion_MK",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_subregion_lk <- make_reef_state_barplot(
  data = reef_state_data %>% filter(SUB_REGION_PLOT == "LK"),
  plot_title = "LK - Proportional Reef State",
  output_stub = "reef_state_subregion_LK",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_subregion_drto <- make_reef_state_barplot(
  data = reef_state_data %>% filter(SUB_REGION_PLOT == "DRTO"),
  plot_title = "DRTO - Proportional Reef State",
  output_stub = "reef_state_subregion_DRTO",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_subregion_sefcri
p_reef_state_subregion_bisc
p_reef_state_subregion_uk
p_reef_state_subregion_mk
p_reef_state_subregion_lk
p_reef_state_subregion_drto
```

## Regressions
### Coral Cover
```{r subregional-coralCover-reg, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_coral_cover_regression <- make_regression_plot(
  data = subregional_data,
  x_var = "hardCoral_PrctCvr",
  x_label = "Coral Cover (%)",
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  group_var = "SUB_REGION_PLOT",
  color_values = subregion_colors,
  legend_title = "Sub-region",
  output_stub = "subregional_regression_netG_vs_coral_cover",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_coral_cover_regression

p_subregional_coral_cover_faceted_regression <- make_faceted_regression_plot(
  data = subregional_data,
  x_var = "hardCoral_PrctCvr",
  x_label = "Coral Cover (%)",
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  group_var = "SUB_REGION_PLOT",
  color_values = subregion_colors,
  legend_title = "Sub-region",
  output_stub = "subregional_faceted_regression_netG_vs_coral_cover",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_coral_cover_faceted_regression
```

### Parrotfish Biomass
```{r subregional-parrotBio-reg, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_parrotfish_biomass_regression <- make_regression_plot(
  data = subregional_data,
  x_var = "parrotfish_Biomass",
  x_label = "Parrotfish Biomass",
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  group_var = "SUB_REGION_PLOT",
  color_values = subregion_colors,
  legend_title = "Sub-region",
  output_stub = "subregional_regression_netG_vs_parrotfish_biomass",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_parrotfish_biomass_regression

p_subregional_parrotfish_biomass_faceted_regression <- make_faceted_regression_plot(
  data = subregional_data,
  x_var = "parrotfish_Biomass",
  x_label = "Parrotfish Biomass",
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  group_var = "SUB_REGION_PLOT",
  color_values = subregion_colors,
  legend_title = "Sub-region",
  output_stub = "subregional_faceted_regression_netG_vs_parrotfish_biomass",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_parrotfish_biomass_faceted_regression
```

```{r subregional-parrotDen-reg, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_parrotfish_density_regression <- make_regression_plot(
  data = subregional_data,
  x_var = "parrotfish_Density",
  x_label = "Parrotfish Density",
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  group_var = "SUB_REGION_PLOT",
  color_values = subregion_colors,
  legend_title = "Sub-region",
  output_stub = "subregional_regression_netG_vs_parrotfish_density",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_parrotfish_density_regression

p_subregional_parrotfish_density_faceted_regression <- make_faceted_regression_plot(
  data = subregional_data,
  x_var = "parrotfish_Density",
  x_label = "Parrotfish Density",
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  group_var = "SUB_REGION_PLOT",
  color_values = subregion_colors,
  legend_title = "Sub-region",
  output_stub = "subregional_faceted_regression_netG_vs_parrotfish_density",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_parrotfish_density_faceted_regression
```

## Temporal Trends
### Net Carbonate Production
```{r subregional-net-carbonate-production, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_net_production <- make_subregional_lineplot(
  data = subregional_data,
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  output_stub = "subregional_net_carbonate_production",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_net_production
```

### Coral Cover
```{r subregional-coral-cover, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_coral_cover <- make_subregional_lineplot(
  data = subregional_data,
  y_var = "hardCoral_PrctCvr",
  y_label = "Coral Cover (%)",
  output_stub = "subregional_coral_cover",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_coral_cover
```

### Coral Production
```{r subregional-coral-carbonate-production, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_coral_production <- make_subregional_lineplot(
  data = subregional_data,
  y_var = "hardCoral_G",
  y_label = "Coral Carbonate Production",
  output_stub = "subregional_coral_carbonate_production",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_coral_production
```

### CCA Cover
```{r subregional-cca-cover, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_cca_cover <- make_subregional_lineplot(
  data = subregional_data,
  y_var = "cca_PrctCvr",
  y_label = "CCA Cover",
  output_stub = "subregional_cca_cover",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_cca_cover
```

### CCA Production
```{r subregional-cca-carbonate-production, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_cca_production <- make_subregional_lineplot(
  data = subregional_data,
  y_var = "cca_G",
  y_label = "CCA Carbonate Production",
  output_stub = "subregional_cca_carbonate_production",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_cca_production
```

### Parrotfish Erosion
```{r subregional-parrotfish, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_parrotfish_erosion <- make_subregional_lineplot(
  data = subregional_data,
  y_var = "parrotfish_G",
  y_label = "Parrotfish Erosion",
  output_stub = "subregional_parrotfish_erosion",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_parrotfish_erosion
```

### Parrotfish Biomass
```{r subregional-parrotfish-biomass, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_parrotfish_biomass <- make_subregional_lineplot(
  data = subregional_data,
  y_var = "parrotfish_Biomass",
  y_label = "Parrotfish Biomass",
  output_stub = "subregional_parrotfish_biomass",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_parrotfish_biomass
```

### Parrotfish Density
```{r subregional-parrotfish-density, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_parrotfish_density <- make_subregional_lineplot(
  data = subregional_data,
  y_var = "parrotfish_Density",
  y_label = "Parrotfish Density",
  output_stub = "subregional_parrotfish_density",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_parrotfish_density
```

### Microbioerosion
```{r subregional-microbioerosion, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_microbioerosion <- make_subregional_lineplot(
  data = subregional_data,
  y_var = "microbioerosion_G",
  y_label = "Microbioerosion",
  output_stub = "subregional_microbioerosion",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_microbioerosion
```

### Macrobioerosion
```{r subregional-macrobioerosion, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_macrobioerosion <- make_subregional_lineplot(
  data = subregional_data,
  y_var = "macrobioerosion_G",
  y_label = "Macrobioerosion",
  output_stub = "subregional_macrobioerosion",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_macrobioerosion
```

### Urchins
```{r subregional-urchin erosion, echo = FALSE, fig.width = 8, fig.height = 5}
p_subregional_urchins <- make_subregional_lineplot(
  data = subregional_data,
  y_var = "urchin_G",
  y_label = "Urchin Erosion",
  output_stub = "subregional_urchin",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_subregional_urchins
```




# Habitat Type
## Carbonate Budget
```{r habitat-carbonate-production-bars, echo = FALSE, fig.width = 11, fig.height = 4.8}
p_habitat_inshore_carbonate_bars <- make_carbonate_barplot(
  data = habitat_data %>% filter(HABITAT_PLOT == "Inshore"),
  plot_title = "Inshore - Carbonate Production",
  output_stub = "habitat_Inshore_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_habitat_midchannel_carbonate_bars <- make_carbonate_barplot(
  data = habitat_data %>% filter(HABITAT_PLOT == "MidChannel"),
  plot_title = "MidChannel - Carbonate Production",
  output_stub = "habitat_MidChannel_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_habitat_offshore_carbonate_bars <- make_carbonate_barplot(
  data = habitat_data %>% filter(HABITAT_PLOT == "Offshore"),
  plot_title = "Offshore - Carbonate Production",
  output_stub = "habitat_Offshore_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_habitat_forereef_carbonate_bars <- make_carbonate_barplot(
  data = habitat_data %>% filter(HABITAT_PLOT == "Forereef"),
  plot_title = "Forereef - Carbonate Production",
  output_stub = "habitat_Forereef_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_habitat_lagoon_carbonate_bars <- make_carbonate_barplot(
  data = habitat_data %>% filter(HABITAT_PLOT == "Lagoon"),
  plot_title = "Lagoon - Carbonate Production",
  output_stub = "habitat_Lagoon_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_habitat_bank_carbonate_bars <- make_carbonate_barplot(
  data = habitat_data %>% filter(HABITAT_PLOT == "Bank"),
  plot_title = "Bank - Carbonate Production",
  output_stub = "habitat_Bank_carbonate_production_bars",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

print(p_habitat_inshore_carbonate_bars)
print(p_habitat_midchannel_carbonate_bars)
print(p_habitat_offshore_carbonate_bars)
print(p_habitat_forereef_carbonate_bars)
print(p_habitat_lagoon_carbonate_bars)
print(p_habitat_bank_carbonate_bars)
```

## Budget State
```{r reef-state-habitat-type, echo = FALSE, fig.width = 8, fig.height = 5}
p_reef_state_habitat_inshore <- make_reef_state_barplot(
  data = reef_state_data %>% filter(HABITAT_PLOT == "Inshore"),
  plot_title = "Inshore - Proportional Reef State",
  output_stub = "reef_state_habitat_Inshore",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_habitat_midchannel <- make_reef_state_barplot(
  data = reef_state_data %>% filter(HABITAT_PLOT == "MidChannel"),
  plot_title = "MidChannel - Proportional Reef State",
  output_stub = "reef_state_habitat_MidChannel",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_habitat_offshore <- make_reef_state_barplot(
  data = reef_state_data %>% filter(HABITAT_PLOT == "Offshore"),
  plot_title = "Offshore - Proportional Reef State",
  output_stub = "reef_state_habitat_Offshore",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_habitat_lagoon <- make_reef_state_barplot(
  data = reef_state_data %>% filter(HABITAT_PLOT == "Lagoon"),
  plot_title = "Lagoon - Proportional Reef State",
  output_stub = "reef_state_habitat_Lagoon",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_habitat_forereef <- make_reef_state_barplot(
  data = reef_state_data %>% filter(HABITAT_PLOT == "Forereef"),
  plot_title = "Forereef - Proportional Reef State",
  output_stub = "reef_state_habitat_Forereef",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_habitat_bank <- make_reef_state_barplot(
  data = reef_state_data %>% filter(HABITAT_PLOT == "Bank"),
  plot_title = "Bank - Proportional Reef State",
  output_stub = "reef_state_habitat_Bank",
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)

p_reef_state_habitat_inshore
p_reef_state_habitat_midchannel
p_reef_state_habitat_offshore
p_reef_state_habitat_lagoon
p_reef_state_habitat_forereef
p_reef_state_habitat_bank
```

## All Sites
### Net Carbonate Production
```{r habitat-type-pooled-net-carbonate-production, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_pooled_net_production <- make_habitat_lineplot(
  data = habitat_data,
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  plot_title = "Pooled Habitat Types - Net Carbonate Production",
  output_stub = "habitat_type_pooled_net_carbonate_production",
  color_values = habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_pooled_net_production
```

### Coral Cover
```{r habitat-type-pooled-coral-cover, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_pooled_coral_cover <- make_habitat_lineplot(
  data = habitat_data,
  y_var = "hardCoral_PrctCvr",
  y_label = "Percent Coral Cover",
  plot_title = "Pooled Habitat Types - Percent Coral Cover",
  output_stub = "habitat_type_pooled_percent_coral_cover",
  color_values = habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_pooled_coral_cover
```

### Parrotfish Biomass
```{r habitat-type-pooled-parrotfish-biomass, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_pooled_parrotfish_biomass <- make_habitat_lineplot(
  data = habitat_data,
  y_var = "parrotfish_Biomass",
  y_label = "Parrotfish Biomass",
  plot_title = "Pooled Habitat Types - Parrotfish Biomass",
  output_stub = "habitat_type_pooled_parrotfish_biomass",
  color_values = habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_pooled_parrotfish_biomass
```


## Biscayne
### Net Carbonate Production
```{r habitat-type-bisc-net-carbonate-production, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_bisc_net_production <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "BISC",
      HABITAT_PLOT %in% c("Inshore", "MidChannel", "Offshore")
    ),
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  plot_title = "BISC Habitat Types - Net Carbonate Production",
  output_stub = "habitat_type_BISC_net_carbonate_production",
  color_values = flk_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_bisc_net_production
```

### Coral Cover
```{r habitat-type-bisc-coral-cover, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_bisc_coral_cover <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "BISC",
      HABITAT_PLOT %in% c("Inshore", "MidChannel", "Offshore")
    ),
  y_var = "hardCoral_PrctCvr",
  y_label = "Percent Coral Cover",
  plot_title = "BISC Habitat Types - Percent Coral Cover",
  output_stub = "habitat_type_BISC_percent_coral_cover",
  color_values = flk_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_bisc_coral_cover
```

### Parrotfish Biomass
```{r habitat-type-bisc-parrotfish-biomass, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_bisc_parrotfish_biomass <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "BISC",
      HABITAT_PLOT %in% c("Inshore", "MidChannel", "Offshore")
    ),
  y_var = "parrotfish_Biomass",
  y_label = "Parrotfish Biomass",
  plot_title = "BISC Habitat Types - Parrotfish Biomass",
  output_stub = "habitat_type_BISC_parrotfish_biomass",
  color_values = flk_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_bisc_parrotfish_biomass
```


## Upper Keys
### Net Carbonate Production
```{r habitat-type-uk-net-carbonate-production, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_uk_net_production <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "UK",
      HABITAT_PLOT %in% c("Inshore", "MidChannel", "Offshore")
    ),
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  plot_title = "UK Habitat Types - Net Carbonate Production",
  output_stub = "habitat_type_UK_net_carbonate_production",
  color_values = flk_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_uk_net_production
```

### Coral Cover
```{r habitat-type-uk-coral-cover, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_uk_coral_cover <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "UK",
      HABITAT_PLOT %in% c("Inshore", "MidChannel", "Offshore")
    ),
  y_var = "hardCoral_PrctCvr",
  y_label = "Percent Coral Cover",
  plot_title = "UK Habitat Types - Percent Coral Cover",
  output_stub = "habitat_type_UK_percent_coral_cover",
  color_values = flk_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_uk_coral_cover
```

### Parrotfish Biomass
```{r habitat-type-uk-parrotfish-biomass, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_uk_parrotfish_biomass <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "UK",
      HABITAT_PLOT %in% c("Inshore", "MidChannel", "Offshore")
    ),
  y_var = "parrotfish_Biomass",
  y_label = "Parrotfish Biomass",
  plot_title = "UK Habitat Types - Parrotfish Biomass",
  output_stub = "habitat_type_UK_parrotfish_biomass",
  color_values = flk_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_uk_parrotfish_biomass
```


## Middle Keys
### Net Carbonate Production
```{r habitat-type-mk-net-carbonate-production, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_mk_net_production <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "MK",
      HABITAT_PLOT %in% c("Inshore", "MidChannel", "Offshore")
    ),
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  plot_title = "MK Habitat Types - Net Carbonate Production",
  output_stub = "habitat_type_MK_net_carbonate_production",
  color_values = flk_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_mk_net_production
```

### Coral Cover
```{r habitat-type-mk-coral-cover, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_mk_coral_cover <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "MK",
      HABITAT_PLOT %in% c("Inshore", "MidChannel", "Offshore")
    ),
  y_var = "hardCoral_PrctCvr",
  y_label = "Percent Coral Cover",
  plot_title = "MK Habitat Types - Percent Coral Cover",
  output_stub = "habitat_type_MK_percent_coral_cover",
  color_values = flk_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_mk_coral_cover
```

### Parrotfish Biomass
```{r habitat-type-mk-parrotfish-biomass, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_mk_parrotfish_biomass <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "MK",
      HABITAT_PLOT %in% c("Inshore", "MidChannel", "Offshore")
    ),
  y_var = "parrotfish_Biomass",
  y_label = "Parrotfish Biomass",
  plot_title = "MK Habitat Types - Parrotfish Biomass",
  output_stub = "habitat_type_MK_parrotfish_biomass",
  color_values = flk_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_mk_parrotfish_biomass
```


## Lower Keys
### Net Carbonate Production
```{r habitat-type-lk-net-carbonate-production, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_lk_net_production <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "LK",
      HABITAT_PLOT %in% c("Inshore", "MidChannel", "Offshore")
    ),
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  plot_title = "LK Habitat Types - Net Carbonate Production",
  output_stub = "habitat_type_LK_net_carbonate_production",
  color_values = flk_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_lk_net_production
```

### Coral Cover
```{r habitat-type-lk-coral-cover, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_lk_coral_cover <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "LK",
      HABITAT_PLOT %in% c("Inshore", "MidChannel", "Offshore")
    ),
  y_var = "hardCoral_PrctCvr",
  y_label = "Percent Coral Cover",
  plot_title = "LK Habitat Types - Percent Coral Cover",
  output_stub = "habitat_type_LK_percent_coral_cover",
  color_values = flk_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_lk_coral_cover
```

### Parrotfish Biomass
```{r habitat-type-lk-parrotfish-biomass, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_lk_parrotfish_biomass <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "LK",
      HABITAT_PLOT %in% c("Inshore", "MidChannel", "Offshore")
    ),
  y_var = "parrotfish_Biomass",
  y_label = "Parrotfish Biomass",
  plot_title = "LK Habitat Types - Parrotfish Biomass",
  output_stub = "habitat_type_LK_parrotfish_biomass",
  color_values = flk_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_lk_parrotfish_biomass
```


## Dry Tortugas
### Net Carbonate Production
```{r habitat-type-drto-net-carbonate-production, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_drto_net_production <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "DRTO",
      HABITAT_PLOT %in% c("Lagoon", "Forereef", "Bank")
    ),
  y_var = "net_G",
  y_label = "Net Carbonate Production",
  plot_title = "DRTO Habitat Types - Net Carbonate Production",
  output_stub = "habitat_type_DRTO_net_carbonate_production",
  color_values = drto_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_drto_net_production
```

### Coral Cover
```{r habitat-type-drto-coral-cover, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_drto_coral_cover <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "DRTO",
      HABITAT_PLOT %in% c("Lagoon", "Forereef", "Bank")
    ),
  y_var = "hardCoral_PrctCvr",
  y_label = "Percent Coral Cover",
  plot_title = "DRTO Habitat Types - Percent Coral Cover",
  output_stub = "habitat_type_DRTO_percent_coral_cover",
  color_values = drto_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_drto_coral_cover
```

### Parrotfish Biomass
```{r habitat-type-drto-parrotfish-biomass, echo = FALSE, fig.width = 8, fig.height = 5}
p_habitat_drto_parrotfish_biomass <- make_habitat_lineplot(
  data = habitat_data %>%
    filter(
      SUB_REGION_PLOT == "DRTO",
      HABITAT_PLOT %in% c("Lagoon", "Forereef", "Bank")
    ),
  y_var = "parrotfish_Biomass",
  y_label = "Parrotfish Biomass",
  plot_title = "DRTO Habitat Types - Parrotfish Biomass",
  output_stub = "habitat_type_DRTO_parrotfish_biomass",
  color_values = drto_habitat_colors,
  export_figures = export_figures,
  png_dir = png_dir,
  svg_dir = svg_dir
)
p_habitat_drto_parrotfish_biomass
```
